---
title: "Using vpeval"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using vpeval}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Basic encounter-level metrics (e.g. mortality, length of stay)

Compute basic, encounter-level metrics like mortality and length of stay.
```{r}
library(vpeval)
vpeval_encinfo
vpeval_demog
basic_metrics(enc_info = vpeval_encinfo, demographics = vpeval_demog)
```


## Information-theoretic measures

Compute the mutual information of two discrete variables.
```{r}
head(mtcars)
mi_cluster(mtcars, x_col = "cyl", y_col = "am")
```

## Summary of drugs given

Drug categories are specified by a data frame with columns for `drug` and `category`. The defaults can be loaded from the vpeval package:
```{r}
library(vpeval)
cats = load_drug_categories()
head(cats)
```
The drug events can be summarized by a binary flag indicating whether or not a drug was given:
```{r}
library(vpmunge)
vpmunge_drugs[, c(1,2,5)]
summarize_drug_categories(vpmunge_drugs, categories = cats)
```

## 

